---
title: "Assignment1-1 Chen"
author: "Chloe Chen"
date: "2023-09-08"
output:
  pdf_document: default
  html_document:
    theme: paper
    highlight: textmate
fontsize: 12pt
number_sections: yes
---

Turn in this assignment as an HTML or PDF file to ELMS. Make sure to include the R Markdown or Quarto file that was used to generate it. You should include the questions in your solutions. You may use the qmd file of the assignment provided to insert your answers.

## Git and GitHub

### 1\) Provide the link to the GitHub repo that you used to practice git from Week 1. It should have:

-   Your name on the README file.

-   At least one commit with your name, with a description of what you did in that commit.

* $https://github.com/yqyhhh/Yang-Lou-Chen.git$

=======
## Reading Data

Download both the Angell.dta (Stata data format) dataset and the Angell.txt dataset from this website: <https://stats.idre.ucla.edu/stata/examples/ara/applied-regression-analysis-by-fox-data-files/>

### 2\) Read in the .dta version and store in an object called `angell_stata`.

<<<<<<< HEAD
```{r}
library(haven)
angell_stata<-read_dta("D:/111/SURV727/Yang-Lou-Chen/angell.dta")
head(angell_stata)
```

### 3\) Read in the .txt version and store it in an object called `angell_txt`.

```{r}
angell_txt<-read.table("https://stats.oarc.ucla.edu/wp-content/uploads/2016/02/angell.txt")
head(angell_txt)
```

### 4\) What are the differences between `angell_stata` and `angell_txt`? Are there differences in the classes of the individual columns?

* There are certain variable names in angell_stata, but the column names in angell_txt are simply V1...V5

### 5\) Make any updates necessary so that `angell_txt` is the same as `angell_stata`.

```{r}
colnames(angell_txt)<-c("city","morint","ethhet","geomob","region")
head(angell_txt)
```

### 6\) Describe the Ethnic Heterogeneity variable. Use descriptive statistics such as mean, median, standard deviation, etc. How does it differ by region?

```{r}
mean(angell_stata$ethhet)
median(angell_stata$ethhet)
sd(angell_stata$ethhet)

library(dplyr)
angell_stata%>%
  group_by(region)%>%
  summarize(m=mean(angell_stata$ethhet),
            med=median(angell_stata$ethhet),
            sd=sd(angell_stata$ethhet))
```

## Describing Data

R comes also with many built-in datasets. The "MASS" package, for example, comes with the "Boston" dataset.

### 7\) Install the "MASS" package, load the package. Then, load the Boston dataset.

<<<<<<< HEAD
```{r}
library(MASS)
data(Boston)
```

### 8\) What is the type of the Boston object?
```{r}
head(Boston)
typeof(Boston)
```
* The type of the object is a list.

### 9\) What is the class of the Boston object?
```{r}
class(Boston)
```
* The class id data frame.

### 10\) How many of the suburbs in the Boston data set bound the Charles river?
```{r}
summary(Boston$chas)
nsub<-506*mean(Boston$chas)
nsub
```
* There $35$ suburbs set bound the Charles river.

### 11\) Do any of the suburbs of Boston appear to have particularly high crime rates? Tax rates? Pupil-teacher ratios? Comment on the range of each variable.
```{r}
range_crim <- range(Boston$crim)
cat("Range of crim:", range_crim, "\n")
range_tax <- range(Boston$tax)
cat("Range of tax:", range_tax, "\n")
range_ptratio <- range(Boston$ptratio)
cat("Range of ptratio:", range_ptratio, "\n")

boxplot(Boston$crim, main="Boxplot of crim", 
        xlab="crim", ylab="Values",
        col=c("blue"))
boxplot(Boston$tax, main="Boxplot of tax", 
        xlab="tax", ylab="Values",
        col=c("green"))
boxplot(Boston$tax, main="Boxplot of ptratio", 
        xlab="ptratio", ylab="Values",
        col=c("red"))
```


* The range of crime is $[0.00632, 88.9762]$; the range of tax is $[187, 711]$; the range of ptratio is $[12.6, 22]$.
* As we can see from the ranges and box-plots, there are particularly high crime rates in several suburbs.
* That doesn't exist in the other two viriables. The range of tax is larger than ptratio, but there are no outliers occur. ptratio is the most compactly distributed data, with little difference between suburbs on this variable.


### 12\) Describe the distribution of pupil-teacher ratio among the towns in this data set that have a per capita crime rate larger than 1. How does it differ from towns that have a per capita crime rate smaller than 1?
```{r}
subset1 <- subset(Boston, Boston$crim > 1)
subset2 <- subset(Boston, Boston$crim <= 1)

#summary
summary(subset1$ptratio)
summary(subset2$ptratio)
var(subset1$ptratio)
var(subset2$ptratio)

#Box plot
boxplot(subset1$ptratio)
boxplot(subset2$ptratio)

#Histogram
hist(subset1$ptratio)
hist(subset2$ptratio)

#Q-Q plot & Conduct statistical tests
library(ggplot2)
qqnorm(subset1$ptratio, main="ptratio1", ylab="y_{i:n}", xlab="m_{i:n}") 
qqline(subset1$ptratio, col="red",lwd=2)
qqnorm(subset2$ptratio, main="ptratio2", ylab="y_{i:n}", xlab="m_{i:n}") 
qqline(subset2$ptratio, col="blue",lwd=2)
shapiro.test(subset1$ptratio)
shapiro.test(subset2$ptratio)




```
*Measures of Central Tendency*
The pupil-teacher ratio among the towns in this data set that have a per capita crime rate larger than 1 has a mean of $19.29$ and a median of $20.20$.
*Measures of Dispersion*
The pupil-teacher ratio among the towns in this data set that have a per capita crime rate larger than 1 has a variance of $4.484129$.
*Distribution Shape*
In Shapiro-Wilk normality test, p-value < 0.05, and from the histogram, as well as the qq-plot, homeprice does not appear to follow a normal distribution.
*Outliers*
From the box plot we can see that there are $4$ outliers in the distribution.



## Writing Functions

### 13\) Write a function that calculates 95% confidence intervals for a point estimate. The function should be called `my_CI`. When called with `my_CI(2, 0.2)`, the function should print out "The 95% CI upper bound of point estimate 2 with standard error 0.2 is 2.392. The lower bound is 1.608."

```{r}
my_CI<- function(point_estimate,se){
  lower_bound<-point_estimate-1.96*se
  upper_bound<-point_estimate+1.96*se
  text <- paste("The 95% CI upper bound of point estimate", point_estimate, "with standard error", se,"is", upper_bound, ". The lower bound is", lower_bound)
  text
}

ci<-my_CI(2,0.2)
ci
```

*Note: The function should take a point estimate and its standard error as arguments. You may use the formula for 95% CI: point estimate +/- 1.96\*standard error.*

*Note: The function should take a point estimate and its standard error as arguments. You may use the formula for 95% CI: point estimate +/- 1.96\*standard error.*

*Hint: Pasting text in R can be done with:* `paste()` *and* `paste0()`

### 14\) Create a new function called `my_CI2` that does that same thing as the `my_CI` function but outputs a vector of length 2 with the lower and upper bound of the confidence interval instead of printing out the text. Use this to find the 95% confidence interval for a point estimate of 0 and standard error 0.4.

```{r}
my_CI2<- function(point_estimate,se){
  lower_bound<-point_estimate-1.96*se
  upper_bound<-point_estimate+1.96*se
  c(lower_bound,upper_bound)
}

ci<-my_CI2(0,0.4)
ci

```

### 15\) Update the `my_CI2` function to take any confidence level instead of only 95%. Call the new function `my_CI3`. You should add an argument to your function for confidence level.

```{r}
my_CI3 <- function(point_estimate, se, confidence_level) {
  if (confidence_level <= 0 || confidence_level >= 1) {
    stop("Confidence level must be between 0 and 1")
  }
  
  z_value <- qnorm(1 - (1 - confidence_level) / 2)
  
  lower_bound <- point_estimate - z_value * se
  upper_bound <- point_estimate + z_value * se
  
  c(lower_bound, upper_bound)
}

ci_90 <- my_CI3(0, 0.4, 0.90)
print(ci_90)

ci_99 <- my_CI3(0, 0.4, 0.99)
print(ci_99)
```

*Hint: Use the* `qnorm` *function to find the appropriate z-value. For example, for a 95% confidence interval, using* `qnorm(0.975)` *gives approximately 1.96.*

### 16\) Without hardcoding any numbers in the code, find a 99% confidence interval for Ethnic Heterogeneity in the Angell dataset. Find the standard error by dividing the standard deviation by the square root of the sample size.

<<<<<<< HEAD
```{r}
se_ethhet <- sd(angell_stata$ethhet)/sqrt(nrow(angell_stata))
mean_ethhet <- mean(angell_stata$ethhet)
ethhetCI<-my_CI3(mean_ethhet, se_ethhet, 0.99)
ethhetCI
```
* The 99% confidence interval for Ethnic Heterogeneity is $[23.35425, 39.38993]$.

### 17\) Write a function that you can `apply` to the Angell dataset to get 95% confidence intervals. The function should take one argument: a vector. Use if-else statements to output NA and avoid error messages if the column in the data frame is not numeric or logical.

```{r}
my_CI4 <- function(column) {
  if (is.numeric(column) |is.logical(column)) {
    mean_value <- mean(column, na.rm = TRUE)
    se <- sqrt(var(column, na.rm = TRUE) / length(column))
    z_value <- qnorm(0.975)  # 95% confidence interval
    
    lower_bound <- mean_value - z_value * se
    upper_bound <- mean_value + z_value * se
    
    return(c(lower_bound, upper_bound))
  } else {
    return(NA)
  }
}


result <- apply(angell_stata, 2, my_CI4) ## Apply this function to each column of Agell

result

```
```{r}
is.numeric(angell_stata$morint)
```

